---
title: "HousePriceKingCounty"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
install.packages("dplyr")
install.packages("ggplot2")
install.packages("corrplot")
library(corrplot)
library("ggplot2")
library("dplyr")
```

## Daten einlesen
Dataset von Kaggle einlesen und ausgeben. 

```{r dataset}
house_prices <- read.csv("kc_house_data.csv")
View(house_prices)
str(house_prices)
dim(house_prices)

# Genaueres Betrachten des Datensatzes
# Übersicht über den Datensatz und die jeweiligen einzigartigen Werte pro Variable
sapply(house_prices, function(x) length(unique(x)))

# Überprüfen auf Vollständigkeit des Datensatzes
table(complete.cases(house_prices)) 
```

## Tidy data

```{r tidyData}
summary(house_prices)
count(house_prices, bedrooms)
count(house_prices, bathrooms)
```

### Plausibilty check 
``` {r plausiCheck}
df2 <- select(house_prices, id, sqft_living, bedrooms)
df3 <- filter(df2, bedrooms == 33)
View(df3)
a <- df3[1, 2]
b <- df3[1, 3]
c <- a / b 
c * 0.092903
``` 
33 is not a plausible amount of bedrooms because the bedroom itself has only around 5 square meters, we will change it to 3

###Create a copy of house_prices, change bedroom value from 33 to 3,# Eliminate all the data which has bedrooms or bathrooms = 0
```{r copy}
house_prices2 <- house_prices

house_prices2[house_prices2$id==2402100895, "bedrooms"] <- 3

house_prices3<-house_prices2[!(house_prices2$bedrooms==0 | house_prices2$bathrooms==0),]
```

###Duplicate check
```{r duplicateCheck}
dup <- filter(count(house_prices3, id), n!=1)
count(dup, n)
View(dup)

# Sample
sample_check1 <- house_prices3[house_prices3$id == 526059224,]
View(sample_check1)

#-> Value of the features are the same except for the price which had a increase 
sample_check2 <- house_prices3[house_prices3$id == 795000620,]
View(sample_check2)

#-> Value of the features are the same except for the price which had a increase 
sample_check3 <- house_prices3[house_prices3$id == 7504021310,]
View(sample_check3)

# We checked all the sample duplicates and got the result that the value of the features are the same except for
# the price which had a increase. 
```

## Korrelation ohne ID, date

--> nur numerische Variablen. 
Frage: macht es sinn manche Variablen als Faktor umzuwandlen? Wenn ja, mache ich das vor oder nach der Korrelation?
```{r correlation }

house_prices4 <- subset(house_prices3, select=c(price,bedrooms, bathrooms,sqft_living,sqft_lot,floors,waterfront,view, condition,grade,sqft_above, sqft_basement, yr_built, yr_renovated, zipcode,lat, long,sqft_living15,sqft_lot15))

corrHouse_prices <- cor(house_prices4)

View(corrHouse_prices)

corrplot(corrHouse_prices)
cor.test(house_prices4$price, house_prices4$bedrooms)
cor.test(house_prices4$price, house_prices4$bathrooms)
cor.test(house_prices4$price, house_prices4$sqft_living)
cor.test(house_prices4$price, house_prices4$sqft_lot)
cor.test(house_prices4$price, house_prices4$floors)
cor.test(house_prices4$price, house_prices4$view)
cor.test(house_prices4$price, house_prices4$condition)
cor.test(house_prices4$price, house_prices4$grade)
cor.test(house_prices4$price, house_prices4$sqft_above)
cor.test(house_prices4$price, house_prices4$sqft_basement)
cor.test(house_prices4$price, house_prices4$yr_built)
cor.test(house_prices4$price, house_prices4$yr_renovated)
cor.test(house_prices4$price, house_prices4$zipcode)
cor.test(house_prices4$price, house_prices4$lat)
cor.test(house_prices4$price, house_prices4$long)
cor.test(house_prices4$price, house_prices4$sqft_living15)
cor.test(house_prices4$price, house_prices4$sqft_lot15)
```

## Plotting

### Price Distribution
```{r priceDistribution, echo=FALSE}
ggplot(house_prices4,aes(x=price))+
  geom_freqpoly(binwidth = 500)+
  xlab('Price')+
  ylab('Count')+
  ggtitle('Price Distribution')
# more number of houses cost in the range of 0 to 1.6 M

# converting Price column 
convertPrice = log10(house_prices4$price)     
ggplot(house_prices4,aes(convertPrice))+
  geom_histogram(fill='green',binwidth = 0.10)+
  xlab('Price')+
  ylab('Count')+
  ggtitle('Price Distribution')

ggplot(house_prices4,aes(price))+
  geom_boxplot()
  ggtitle('Price Distribution')
  
ggplot(house_prices4,aes(convertPrice))+
  geom_boxplot()
  ggtitle('Price Distribution')

```
###sqft_Living
```{r sqftLiving}
ggplot(house_prices4,aes(sqft_living))+
  geom_boxplot()+
  ggtitle('Distribution of Square Feet Living')

#Price vs. Sqft_living 
ggplot(house_prices4,aes(x=sqft_living,y=price))+
  geom_jitter(color='blue')+
  xlab('Square Feet Living')+
  ylab('Price')+
  ggtitle('Price vs Square Feet Living')
```
###Sqft_above
```{r sqftAbove}
ggplot(house_prices4,aes(sqft_above))+
  geom_freqpoly(binwidth=50,color = 'red')+
  xlab('Square Feet Above')+
  ggtitle("Distribution of square feet above")

#Price vs. Sqft_above
ggplot(house_prices4,aes(x=sqft_above,y=price))+
  geom_jitter(color = 'blue')+
  xlab('Square Feet Above')+
  ylab('Price')+
  ggtitle('Price vs Square feet above')

ggplot(house_prices4,aes(x=sqft_above,y=convertPrice))+
  geom_jitter(color='blue')+
  xlab('Square Feet Above')+
  ylab('ConvertPrice')+
  ggtitle('ConvertPrice vs Square feet above')
```
###bathrooms
``` {r batrooms}

unique(house_prices4$bathrooms)
table(house_prices4$bathrooms)

house_prices4$bathrooms <- as.factor(house_prices4$bathrooms)



ggplot(house_prices4,aes(bathrooms))+
  geom_bar(fill="green")+
  ggtitle('Distribution of bathrooms')

#Price vs. Bathrooms
ggplot(house_prices4, aes(x=bathrooms,y=price))+
  geom_boxplot()+
  ggtitle("Price vs Bathrooms")

ggplot(house_prices4, aes(x=sqft_living, y=price, color=bathrooms))+
  geom_point()+
  ggtitle(" Price vs sqft living on the bases of bathrooms")
```
###bedrooms
```{r bedrooms}
unique(house_prices4$bedrooms)
table(house_prices4$bedrooms)

house_prices4$bedrooms <- as.factor(house_prices4$bedrooms)



ggplot(house_prices4,aes(bedrooms))+
  geom_bar(fill="green")+
  ggtitle('Distribution of bedrooms')

#Price vs. bedooms
ggplot(house_prices4, aes(x=bedrooms,y=price))+
  geom_boxplot()+
  ggtitle("Price vs bedrooms")

ggplot(house_prices4, aes(x=sqft_living, y=price, color=bedrooms))+
  geom_point()+
  ggtitle(" Price vs sqft living on the bases of bedrooms")
```
###condition
```{r condition}
house_prices4$condition <- as.factor(house_prices4$condition)

unique(house_prices4$condition)
table(house_prices4$condition)

ggplot(house_prices4,aes(condition))+
  geom_bar(color = 'green')+
  xlab('condition')+
  ggtitle("Distribution of Condition ")

# Price vs. Condition 
ggplot(house_prices4,aes(x= condition,y= price))+
  geom_boxplot()+
  xlab('condition')+
  ylab('Price')+
  ggtitle("Price vs Condition")


ggplot(house_prices4,aes(x= condition,y= convertPrice))+
  geom_boxplot(color = 'aquamarine4')+
  xlab('Condition')+
  ylab('ConvertPrice')+
  ggtitle("ConvertPrice vs  Condition")

```
Schlussfolgerung: Der Preis ist hoch, wenn der Zustand gut ist

```{r relationship_sqft_living_price_condition}

log_size=log10(house_prices4$sqft_living)
ggplot(house_prices4,aes(x=log_size,y=convertPrice,color=condition))+
  geom_point(size=0.5)+
  facet_wrap(~condition)+
  ggtitle("Log_price vs Log_size for each Condition")
```

### grade
```{r grade}
house_prices4$grade <- as.factor(house_prices4$grade)

unique(house_prices4$grade)
table(house_prices4$grade)

ggplot(house_prices4,aes(grade))+
  geom_bar(color = 'green')+
  xlab('grade')+
  ggtitle("Distribution of Grade ")

# Price vs. Condition 
ggplot(house_prices4,aes(x= grade,y= price))+
  geom_boxplot()+
  xlab('Grade')+
  ylab('Price')+
  ggtitle("Price vs Grade")


ggplot(house_prices4,aes(x= grade,y= convertPrice))+
  geom_boxplot(color = 'blue')+
  xlab('Grade')+
  ylab('ConvertPrice')+
  ggtitle("ConvertPrice vs  Grade")
```